AFQ-Insight

### 2019-12-01 reports/manuscript/sections/results.tex
More figure captions. Section titles.

\subsection*{SGL of tractometry data in a regression setting}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right. The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the tracts. The left cingulum cingulate (A) and forceps minor (B) are highlighted. Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
    }
    \label{fig:regress-beta}
\end{figure}

@@

\subsection*{Classification for ALS detection}

@@

    \caption{{\bf Prediction of ALS status.}
        Left: Classification probabilities for each subject's ALS diagnosis.
        Controls are on the left while patients are on the right. Predicted
        controls are in blue and predicted patients are in red. Thus, false
        positive are represented as red dots on the left, while false negatives
        are represented as blue dots on the right. The SGL algorithm achieves
        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
        coefficients are presented on a skeleton of the major tracts. The brain
        is oriented with the right hemisphere to our left and anterior out of
        the page. As expected large negative coefficients are in the FA of the
        corticospinal tract (and particularly right CST, here to the left)}
    \label{fig:class-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
    \caption{{\bf Coefficients with FA tract profiles}
       }
    \label{fig:class-profiles}
\end{figure}

\begin{figure}[!h]
    \centering
        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
    \caption{{\bf Mis-classifications}
       They make sense}
    \label{fig:class-errors}
\end{figure}

>>>>

\subsection*{SGL accurately predicts age from tractometry data in a regression setting}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{regression_beta_annotated.pdf}
    \includegraphics[width=0.67\textwidth]{regression_tract_profiles.pdf}
    \caption{{\bf Feature importance for predicting age from tractometry.} Left: A skeletonized display of the main brain tracts analyzed, with anterior facing up, and right hemisphere on the right. The $\hat{\beta}$ coefficients displayed in blue (negative) to red (positive) are for measurements of FA along the length of the tracts. The left cingulum cingulate (A) and forceps minor (B) are highlighted. Right: the FA (in shades of blue and green) and the $beta$ coefficients (dashed) in (A) left cingulum and (B) forceps minor.
    }
    \label{fig:regress-beta}
\end{figure}

@@

\subsection*{SGL accurately detects ALS in tractometry data in a classification setting}

@@

    \caption{{\bf SGL accurately predicts ALS.}
        Left: Classification probabilities for each subject's ALS diagnosis.
        Controls are on the left while patients are on the right. Predicted
        controls are in blue and predicted patients are in red. Thus, false
        positive are represented as red dots on the left, while false negatives
        are represented as blue dots on the right. The SGL algorithm achieves
        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
        coefficients are presented on a skeleton of the major tracts. The brain
        is oriented with the right hemisphere to our left and anterior out of
        the page. As expected large negative coefficients are in the FA of the
        corticospinal tract (and particularly right CST, here to the left)}
    \label{fig:class-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
    \caption{{\bf Model coefficients mirror FA differences}. The places along the
       length of the corticospinal tract where $\hat{\beta}$ coefficients for FA
       (dashed line, right axis) have large negative values correspond to the
       locations of substantial differences between the ALS (green) and control
       (orange) FA (shaded area indicates standard error of the mean).}
    \label{fig:class-profiles}
\end{figure}

\begin{figure}[!h]
    \centering
        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
    \caption{{\bf Model mis-classifications correspond to features identified by the model}.
       They make sense}
    \label{fig:class-errors}
\end{figure}
